Spatial Analysis

### 2021-11-29 Scripts/spatial_analisis.Rmd
Fixed color issue for F5

state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
                               wes_palette(n = 5, name = "Darjeeling2"),
                               # wes_palette(n = 2, name = "GrandBudapest1")
                  "#FD6467"
                  )

@@

## Regulatory units result

@@

# Plot me
ssp_area <-
  ggplot(state_fit) +
  geom_area(
    aes(
      x = year,
      y = round(RMean),
      fill = order
      # fill = state
    )
  ) +
  geom_area(data = historic_periods,
             aes(
               x = year,
               y = n,
               color = period
             ),
             # fill = "gray90",
             alpha = 0.3,
            stat = "identity"
             ) +

  ylab("Propotion (10 yrs running average)") +
  # viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
  scale_fill_manual(
    "State\n(Latitudinal order)",
    values = state_pallet,
    labels = state_fit %>% arrange(order) %>%  pull(state) %>% unique()
  ) +
    scale_color_manual("",values = "grey90"
  ) +
  facet_grid(spp~spatial) +
  scale_x_continuous(breaks = seq(1979,2015,9),limits = c(1979,2015))+
  xlab("Year") +
  my_ggtheme_p(leg_pos = "right", hjust = 0.9,ax_tx_s = 14,leg_tx_s = 16, leg_tl_s = 18,ax_tl_s = 18,facet_tx_s = 16) +
  theme(legend.key.width = unit(1,"line"),
        legend.title.align=0.5)

>>>>

state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
                               wes_palette(n = 5, name = "Darjeeling2"),
                  "#FD6467"
                  )

length(state_pallet)

barplot(c(1,2,3,4,5,6,7,8,9,10,11), col=state_pallet)

@@

## F1 Regulatory units result

@@

# Plot me
ssp_area <-
  ggplot(state_fit) +
  geom_area(
    aes(
      x = year,
      y = round(RMean),
      # fill = abrev
      fill = state
    )
  ) +
  geom_area(data = historic_periods,
             aes(
               x = year,
               y = n,
               color = period
             ),
             # fill = "gray90",
             alpha = 0.3,
            stat = "identity"
             ) +
  ylab("Propotion (10 yrs running average)") +
  # viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
  scale_fill_manual(
    "State\n(Latitudinal order)",
    values = c(state_pallet[1:10],state_pallet[10]),
                      labels = state_fit %>% arrange(desc(order)) %>%  pull(state) %>% unique()
  ) +
    scale_color_manual("",values = "grey90"
  ) +
  facet_grid(spp~spatial) +
  scale_x_continuous(breaks = seq(1979,2015,9),limits = c(1979,2015))+
  xlab("Year") +
  my_ggtheme_p(leg_pos = "right", hjust = 0.9,ax_tx_s = 14,leg_tx_s = 16, leg_tl_s = 18,ax_tl_s = 18,facet_tx_s = 16) +
  theme(legend.key.width = unit(1,"line"),
        legend.title.align=0.5)
